\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{trees}
\pagestyle{fancy}

\lhead{MTH 201 (Calculus)}
\chead{Activities: Elementary Derivative Rules}
\rhead{2018-10-01}

\begin{document}

\noindent
\textbf{Instructions:} In this activity you'll be working in threes (not fours!) to practice the basic rules and apply them to common situations. Each group of three will be given one of the exercises from each group and asked to work out their answers in full at the board or on one of the big sticky notes. Be ready to show all your work and explain all your steps. 

\bigskip

\subsection*{Part 1: Basic Practice}

Find the derivative for each of the following. Each group will be given one of these to present at the board or on the wall. Do all of these, but do your group's problem first and be ready to explain. 


\begin{enumerate}
    \item $a(x) = 7x^{-3} + x^2 + 5$
    \item $b(t) = \sqrt[4]{t} + \sqrt[3]{t}$
    \item $c(t) = 6 \sqrt{t} + \dfrac{1}{\sqrt{t}}$
    \item $d(x) = 3e^x - x^3 + 3x$
    \item $f(x) = \dfrac{\sqrt{x} + 1}{x}$ (Hint: Simplify first.) 
    \item $g(x) = x^3 + 3^x + x^e + e^x + e$
    \item $T = 3C^{2/3}$ (Find $dT/dC$) 
    \item $z(k) = 3 \sin(k) - \pi \cos(k)$
    
\end{enumerate}

\subsection*{Part 2: Basic Applications}

Each group will be given one of these to present at the board or on the wall. Do all of these, but do your group's problem first and be ready to explain.

\begin{enumerate}
    \item Find the slope of the tangent line to the graph of $y = \frac{3}{x^4}$ at $x=2$. 
    \item Find the equation (not just the slope) of the tangent line to the graph of $y = 4x - 16x^2$ at $x = 2$. 
    \item The height of a ball above the ground after $t$ seconds is given by $s(t) = 48 + 32 t - 16 t^2$ where $s$ is measured in feet. Find the position, velocity, and acceleration of the ball after 1 second. Put correct units on your answers. 
    \item With an initial deposit of \$100, the balance in a bank account after $t$ years is $f(t) = 100(1.08)^t$ dollars. Find the amount of money in the account and the rate at which the account balance is changing, after $5$ years. Round answers to two decimal places because it's money. 
\end{enumerate}

\subsection*{Part 3: Bonus round}

If you finish all of the above and want more practice or an additional challenge, try these: 
\begin{enumerate}
    \item Find the points where the tangent line to the graph of $y = x^2 + 3x - 7$ is parallel to the line $y = 4x + 2$. 
    \item Find the points where the tangent line to the graph of $y = x - 3x^2$ is horizontal. 
    \item Find values of $a$ and $b$ such that $p(x) = x^2 + ax + b$ satisfies the conditions $p(1) = 0$ and $p'(1) = 4$.
    \item Find all the points where the graph of $y = \sin(x) + \cos(x)$ has a horizontal tangent line. (Note there are infinitely many of these, so state a pattern or formula.) 
\end{enumerate}


\end{document}